DNNNNR0: How to Avoid OOTA Without Really Trying

### 2025-03-27 paper/ootavacuous.tex
ootavacuous: Add future work on speculative loads
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

Additional future work could:
(1)~Extend these results to some classes of interpreters and just-in-time
compilers (JITs) on
one hand, and to link-time optimization (LTO) on the other;
(2)~Consider various classes of global analysis, such as
demonstrating that a given expression will always evaluate to a constant;
(3)~Examine the possibility of ``flattening'' optimizations that combine
multiple threads into one;
(4)~Explore cases in which semantic dependencies must be absolute,
not relative to any particular compiler;
(5)~Include the effects of input and output or other operations which
can vary from one execution to another; and
(6)~Delineate more precisely the limits of permissible behavior for
quasi-volatile object accesses.
This last item may well shed additional light on the dangers of
optimizations involving non-volatile atomic operations beyond the cautions
outlined in
Section~\ref{sec:Inventing Atomic Loads Can Cause Errors and
Destroy Semantic Dependencies}.

>>>>

Additional future work could:
(1)~Extend these results to some classes of interpreters and just-in-time
compilers (JITs) on
one hand, and to link-time optimization (LTO) on the other;
(2)~Relax quasi-volatile semantics to permit limited load speculation,
for example, use of conditional-move instructions in cases where the
source code conditionally consumes the results of the atomic load;
(3)~Consider various classes of global analysis, such as
demonstrating that a given expression will always evaluate to a constant;
(4)~Examine the possibility of ``flattening'' optimizations that combine
multiple threads into one;
(5)~Explore cases in which semantic dependencies must be absolute,
not relative to any particular compiler;
(6)~Include the effects of input and output or other operations which
can vary from one execution to another; and
(7)~Delineate more precisely the limits of permissible behavior for
quasi-volatile object accesses.
This last item may well shed additional light on the dangers of
optimizations involving non-volatile atomic operations beyond the cautions
outlined in
Section~\ref{sec:Inventing Atomic Loads Can Cause Errors and
Destroy Semantic Dependencies}.
